Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-11-28 formally.tex
rewording comment about witnesses

  \item If $\hana{\hGamma}{\hexp}{\htau}$ and $\removeSel{\zexp}=\hexp$
    then there exists some $\bar\alpha$ such that
    $\bar\alpha~\mathsf{movements}$ and
    $\performAnaI{\hGamma}{\zwsel{\hexp}}{\htau}{\bar\alpha}{\zexp}$.
  \end{enumerate}
\end{lemma}
Theorem \ref{thrm:reachability} follows by straightforward composition of
these two lemmas. (Of course, the witness produced is not usually the most efficient way
to move between two locations.)

>>>>

  \item If $\hana{\hGamma}{\hexp}{\htau}$ and $\removeSel{\zexp}=\hexp$
    then there exists some $\bar\alpha$ such that
    $\bar\alpha~\mathsf{movements}$ and
    $\performAnaI{\hGamma}{\zwsel{\hexp}}{\htau}{\bar\alpha}{\zexp}$.
  \end{enumerate}
\end{lemma}
Theorem \ref{thrm:reachability} follows by straightforward composition of
these two lemmas. The proofs we give of these three theorems in the
mechanization do not produce the shortest sequence of actions to witness
reachability, which would resemble something like a lowest common ancestor
computation. In future versions of Hazelnut that use the produced witnesses
for automatic tool support it may make sense to engineer these proofs
differently; here we are only concerned with whether the theorems are true.
